---
title: "Data Exploration: Europe Brent Spot Price FOB"
author: "Enrique Pérez Herrero"
date: "January 9, 2017"
output: 
  html_document: 
    highlight: tango
    number_sections: yes
    theme: cosmo
    toc: yes
---

# SUMMARY

Europe Brent Spot Price FOB (Dollars per Barrel) [https://www.eia.gov/dnav/pet/hist/LeafHandler.ashx?n=PET&s=rbrte&f=D](https://www.eia.gov/dnav/pet/hist/LeafHandler.ashx?n=PET&s=rbrte&f=D)


# LOAD DATA

## Load Packages

```{r setup, message=FALSE}
library(readxl)
library(plotly)
```

## Data URL and file path

```{r}
data_url <- "https://www.eia.gov/dnav/pet/hist_xls/RBRTEd.xls"
data_file <- basename(data_url)
data_dir <- "data"
data_path <- paste(data_dir, data_file, sep = "/")
```

## Download EXCEL with data

```{r}
if(!file.exists(data_path)) {
  download.file(data_url, destfile = data_path, method = "wget")
}
```

## Read Data

```{r}
brent_prices <- read_excel(data_path, sheet = "Data 1", skip = 2)
brent_prices <- na.omit(brent_prices)
names(brent_prices) <- c("Date", "USD_Barrel")
```

# SUMMARY

```{r}
summary(brent_prices)
```


# PLOT PRICES

## Prices plot

```{r}
plot_ly(data = brent_prices,
        x = ~Date,
        y = ~USD_Barrel,
        type = "scatter",
        mode = "lines") %>%
  layout(title = "Europe Brent Spot Price FOB",
         xaxis = list(title = ""),
         yaxis = list(title = "Price (USD/Barrel)")
         )
```


## Prices Histogram

```{r}
plot_ly(data = brent_prices,
        x = ~USD_Barrel,
        type = "histogram") %>%
  layout(title = "Daily Prices Histogram",
         xaxis = list(title = "Price (USD/Barrel)")
  )
```


# LINKS

* [4-Plot](http://www.itl.nist.gov/div898/handbook/eda/section3/4plot.htm)  
* [R in Time Series: Autocorrelation in R](http://quantlego.com/howto/autocorrelation-in-r/)
* [Forecasting Brent Oil](https://rstudio-pubs-static.s3.amazonaws.com/71505_b67043c08a5f48c2b5797fab525401cb.html)
* [Oil Series in R](http://kukuruku.co/hub/r/oil-series-oil-prices-in-r)
* [Plotting Forecast Objects](https://plot.ly/r/graphing-multiple-chart-types/#plotting-forecast-objects)
* [CRAN Task View: Time Series Analysis](https://cran.r-project.org/web/views/TimeSeries.html)
* [Forecasting the Price of Oil
Ron Alquist, Lutz Kilian, and Robert J. Vigfusson](https://www.federalreserve.gov/pubs/ifdp/2011/1022/ifdp1022.pdf)
* [Forecasting Model for Crude Oil Price Using Artificial Neural Networks and Commodity Futures Prices](https://arxiv.org/abs/0906.4838)